The controlled choice design and private paternalism in pawnshop borrowing - STATA documentation

### 2024-06-07 Restud submission/donde_restud.tex
prepare for restud submission

\title{The forcing-choice design and paternalism in pawnshop borrowing\thanks{We want to thank Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, Anett John David Laibson, Aprajit Mahajan, Matt Rabin, Mauricio Romero, Charlie Sprenger, Chris Udry, and seminar participants at ITAM, USC, MSU, and UCSD provided valuable feedback. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.  Research assistance was financed through faculty grants at ITAM. Our research partner had no say in the design or results of the experiment.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
\date{This draft:  \today \\[2 cm]}

@@

\begin{abstract}
We explore paternalism in the important high-default pawnlending context. We use a novel one-stage, three-armed RCT, including forced and voluntary treatment arms, to point-identify the effects of commitment on both the treated \textit{and the untreated} simultaneously. We find that forcing borrowers into contracts with a regular repayment structure decreases the financial cost of pawn loans by 22\% and increases the likelihood of recovering their pawn by 15\%. However, only 11\% of borrowers choose such contracts. We find that borrowers who would not choose frequent payments would benefit substantially from getting such contracts, as much as those freely choosing them (no selection on gains).  A paternalistic policy of universal forced commitment archives similar benefits to personalized ML targeting. 
\end{abstract}

@@

Pawn loans constitute one of the oldest and most prevalent forms of borrowing \citep{carter2012pawnshops}.
Our partner lender, for example, made over 4 million loans to more than a million clients during in the three years adjacent to our experiment.\footnote{For comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.} 
The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{A large literature shows  stress impairs cognitive function, e.g. \cite{StressReview}.}
%\footnote{There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).  \url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.}

@@

Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches. Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal, \hl{XX\%} of those made payments toward recovery.\footnote{High pawn default rates are common, in the US they oscillate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan. The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent.  In our ``forced commitment'' arm all borrowers are \emph{required} to repay using the same structured monthly contract offered on an opt-in basis in the commitment choice arm. We use the labels commitment and structured payment contract interchangeably.

This design allows us to measure the effects of structured payments, and also the demand for this contractual feature. We demonstrate that it allows us to estimate (under minimal assumptions) the relationship between treatment effects and treatment take-up, a core concern in the econometrics literature. Intuitively, our design can be seen as a two-sided encouragement design, encouraging some borrowers to take and others to not take up structured repayment. In principle, the marginal treatment effect approach allows researchers to use observational data and an excluded instrument to study the relationship between treatment effects and treatment take-up. In practice, unless the instrument has a rich support set, additional modeling assumptions \citep{mogstad2018using} are needed. BDM mechanisms incentivizing choice prior to treatment assignment \citep{becker1964measuring} could be used to tackle this question, with some limitations \citep{bohm1997eliciting,banerji2014detection}. Finally, two-stage designs in the spirit of \cite{KarlanZinman2009} have been used to study related questions \citep{Beaman2023}. Below we compare our novel one-stage design with two-stage ones.

@@

On mechanisms, the monthly payment contract seems to achieve these cost savings by speeding up payments and, interestingly, by generating an early \textit{bifurcation} of borrowers into those that will recover the pawn and those that will not. The former are induced to pay faster, saving on interest; the latter pay less towards loans that ultimately default, hence losing less money when they do. One interpretation is that requiring payments earlier accelerates learning about the feasibility of making such payments, thus reducing overconfidence, a mechanism not discussed much in the literature.

@@

Next, we impose a mild exclusion restriction positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it. In other words, we assume that choosing a contract results in the same potential outcome as being assigned that contract. This is a relatively common if often implicit assumption in causal inference.\footnote{Papers that use variation in compulsory schooling laws to identify the returns to schooling, for example, typically interpret their results as the causal effect of additional \emph{education} rather than additional \emph{forced education}. \cite{chamberlain2011bayesian} uses a closely related assumption to develop a theory of optimal treatment choice.} 
It also has testable implications that we fail to reject in our empirical context.\footnote{See \autoref{sec:testing_exclusion} for details.}
Under this restriction, the controlled choice design point identifies the TOT, TUT, ASG, ASB, and ASL effects described above.  Our estimated TUT effect on financial cost savings is large: \$192 pesos, equivalent to a 10.6 percentage point savings in APR. On average, the borrowers who would \textit{not} choose commitment, would have faced substantially lower financial costs if they had.

In a one-shot interaction, the game between the borrower and the lender is zero-sum. Decreasing financial costs for the borrower means decreasing the lender's profit. However, we find that experiencing the structured payments contract leads to a 6 percentage point increase in repeat borrowing from the lender. A back-of-the-envelope calculation shows that still, the contract reduces lender's profits by \hl{XX\%}, implying that lenders would not offer this contract (as was the case in Mexican pawnshops) if not forced in our context.\footnote{Our partner lender contacted us to evaluate structured payments for two reasons. First, they genuinely wanted to know the causal effects of structured payments but did not know how to estimate them rigorously. Second, our lender operates as a non-profit, donating their earnings to philanthropic aims.}

@@

On the question of what explains the persistence of no-commitment contracts so contrary to borrowers’ interests, there are several candidates. From the demand side, while a simple measure of time inconsistency does not explain the large and positive TUT effect, we show substantial levels of over-optimism among borrowers, the average subjective probability of recovering their pawn is \hl{XX\%}, while the actual average is only \hl{XX\%}. Among borrowers who do not choose commitment, those with the largest estimated benefits from commitment are the individuals who most systematically over-estimate their own probability of repayment without the need to commit, potentially decreasing their demand from commitment. From the supply side, because loans are over-collateralized, the lender in the contract stands to gain the most when borrowers default.  Our partner's \emph{status quo} pawn contract (standard in the industry) gave 70\% of the value of gold collateral in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract, that could be paid back anytime before the loan comes due at no penalty. The fact that the gold pawn is highly liquid, means that the lender makes more profit over three months from a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid). While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.

@@

Our paper makes a number of contributions to the literature. First, %we propose a way to use three-armed experimental structure to recover treatment effects for choosers and non-choosers under minimal assumptions.\footnote{A companion STATA package provides simple, regression-based estimators for each of these causal parameters, along with appropriate cluster-robust standard errors. See \autoref{sec:estimation_inference} for details.}  
to a relatively small literature that sheds light on private paternalism and selection on gains. In the context of food choice, in an very creative paper \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment. In contrast, we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection. In the context of school choice, \cite{Walters} combines a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates. He finds that students who select into more effective schools have smaller treatment effects from attending than those who do not select in. Our approach instead point identifies TUT and TOT and a range of other interesting causal parameters without the need for a structural model, relying instead on relatively weak exclusion restrictions whose testable implications we fail to reject. In the context of agriculture, \cite{Beaman2023} compare the average treatment effect on farm profits from providing \textit{cash grants} to a set of farmers that did not select into getting \textit{loans} to those of average farmers. They do this in a two-stage design, by first offering loans or not to a set of farmers, and then randomizing cash grants among those who would not have received loans. Our paper is complementary in several respects. Because we estimate the average effect of a given treatment for those who did and did not select into that \textit{same} treatment, our design allows us to estimate effects on non-compliers, but on compliers as well, allowing the estimation of selection on gains, selection bias and selection on levels.  \cite{Beaman2023} find that those selecting out of loans have lower average returns to capital, consistent with positive selection. In contrast, we find no evidence of positive selection. Our design could be used in situations where two-stage randomization is not feasible or too costly.\footnote{\cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they identified \emph{two} TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers. This difference is what allows our design to point identify the ASG and related quantities.}

@@

Our study also speaks to recent research on the effects of payment frequency. While experiments in microfinance markets have \textit{not} not found benefits from providing a more regularized repayment environment as we find here \citep{Pande, barboni2023flexible, Field}, these experiments differ from ours in two important ways: they are performed on top of already highly structured micro-finance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \cite{bauer2012behavioral}. These differences may explain why \citep{Pande} finds almost no default in the control group, in stark contrast to our setting of high default. Second, we study \textit{both} take-up and the efficacy of voluntary commitment mechanisms. A number of papers have found low demand for commitment as we do.\footnote{\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}. Others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).} Unlike all of these papers, however, we separately point-identify and estimate the effects of commitment for borrowers who would and \textit{would not} choose it.

%By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.  Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) does not generate adequate demand in this context.

Given their enormous prevalence and the vulnerability of their users, pawn loans are severely understudied; we believe the descriptive information and treatment effects estimates for pawn borrowing are an important contribution. We also believe that the forcing-choice RCT design provides a useful counterpoint to the widely used \cite{KarlanZinman2009} (KZ) designs. As far as we are aware, ours is the only experimental design in the literature simultaneously estimating both the TOT and TUT effects, along with the average selection on gains, without the need for auxiliary structural assumptions. Note that KZ designs do not estimate the TUT effect, which is crucial for evaluating the case for paternalism.\footnote{The KZ design is useful for separating moral hazard from adverse selection when a two-product comparison is relevant, with one being strictly preferable to consumers.  Our design is useful in mapping marginal treatment effects to compliance with a single treatment, particularly in contexts where a) forcing is possible and b) selection subsequent to forcing is low, or is of direct interest to the principal (in that case, our design would still provide useful information to the principal but would not isolate agent-level heterogeneity in the way it does here).}

The remainder of the paper is structured as follows:  Section \ref{context} provides context and defines our main outcome variables. Section \ref{Design} describes the experiment and data sources, and shows pre-treatment balance across arms. Section \ref{Experiment} provides the standard ITT analysis of the experiment, while Section \ref{Choice} shows how to identify, estimate and carry out inference for the TOT, TUT, ASG, ASB and ASL effects under the controlled choice design. Section \ref{Paternalism} investigates why paternalism functions so well in this context and whether it can be more finely targeted and Section \ref{conclusion} concludes.

@@

%\hfill \newline
%\noindent \textbf{Borrowers.} 
\paragraph*{Borrowers.} Borrowers are not completely inexperienced: 87\% of clients in our survey report they have pawned before. %These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
However they are economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months. In terms of triggers and uses of the loan, 89\% said they are pawning because of an emergency, and only 12\% stated it was to be used in a ``non-urgent expense''.  When asked why they are pawning this piece, 5\% responded ``lost a family member'', ``a medical emergency'' (11\%), or ``an urgent expense'' (72\%). Only \hl{XX\%} of borrowers have completed college, 73\% of are women, with an average age of 43 years.

@@

\paragraph*{Gold buying shops.} Gold purchasing shops locate close to our Lender's branches. Branches have an average of \hl{XX} of these shops.

@@

\paragraph*{Overconfidence.} We implemented a baseline survey to \hl{more than 10,000} respondents. In it, we asked borrowers for their subjective probability of recovering the pawn. The average recovery probability is \hl{XX\%}. This contrasts sharply with the actual recovery rate for these same borrowers, \hl{57\%}. Overall 72\% of borrowers report a 100\% probability of repaying their loan.    %Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer. 
%Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.

@@

\subsection{No differential selection and balance}
\label{sec:integrity}

@@

We were aware that the major threat for this study was selection into borrowing based on contract terms. This did \textit{not} happen. We show this in three different ways. First, out of those coming into the branch and filling out the baseline survey, \hl{97\%} end up pawning. This rate is not only high but is also not different across treatment arms. Second, the number of loans per day is not different across arms, showing borrowers did not stop pawning when the forcing arm or choice arm was active.  Third, borrower and loan characteristics are the same across arms, showing that there is no selection on observables.\footnote{Note that is borrowers self-selected based on contract terms, the results would still reflect the overall impact of a treatment for the lender's portfolio. In our case, there is no selection, so we can study the causal effects on borrowers.}

@@

Table \ref{attrition_table_final} shows there are no differences in the number of loans, borrowers, or amount borrowed across arms using administrative data. Each row corresponds to a regression of the dependent variable on indicators for treatment assignment (status quo/control, forced commitment, choice). In the first row (``Take-up'') we use the sample of those who answered the baseline survey (\hl{XXX} subjects) and check which of them pawned based on the administrative data. The dependent variable indicates whether the person pawned. Because this survey was implemented at the entrance of the branch before they knew their treatment assignment, it is a good measure of take-up. The first result is that the overwhelming majority (97\%) take the loan. Second, the same fraction of borrowers take up the loan across treatment arms. This is strong evidence that borrowers did not select deferentially according to the structured payments contractual feature. The remaining rows use only administrative data. For each branch day, we calculate the number of borrowers pawning, the number of pawns used, pawns per borrower, and the total amount borrowed and regress each of those on treatment arms. We again cannot reject that any of those measures of demand are the same across arms.  We also report medians to reduce the influence of outliers.

\begin{table}[H]
\caption{No selection across arms}
\label{attrition_table_final}
\begin{center}
\footnotesize{\input{./Tables/Attrition.tex}}
\end{center}
\scriptsize{Each row in this table 
 corresponds to a regression \hl{at the branch-day level} of each dependent variable against the experimental arms indicators (control, forced commitment, choice). The table reports the coefficients on each of these indicators, as well as the p-value of an F-test of the null hypothesis of equality of the three coefficients. We also report \hl{raw medians} for each arm. \hl{ISAAC, could add not just pesos per loan, but real total lent per branch-day?} %Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.
 }
%\textit{Do file: } \texttt{ss\_att.do}
\end{table}

@@

\begin{table}[H]
\caption{Borrower's characteristics are balanced}
\label{SS_final}
\begin{center}
\resizebox{0.65\textwidth}{!}{
\footnotesize{\input{./Tables/SS.tex}}
}
\end{center}
\scriptsize {Each row in this table corresponds to a regression, where the level of observation is a \hl{borrower that pawned} which we surveyed.  \hl{Surveys were not conducted at the beginning of the experiment}. The dependent variables are displayed in the first column. Each dependent variable is regressed against the experimental arms indicators (control, forced commitment, choice). The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients. ``Subjective value'' of the pawn refers to how much would the client be willing to sell the pawn for in pesos, ``Trouble paying bills'' is an indicator for the borrower reporting having problems paying electricity, water and services in the last 6-months, present bias is constructed as in \cite{Ashraf}; ``Makes buget'' os an indicator for whether the household make expenses budget for the month ahead of time. The subjective probability of recovery was elicited a la Manski (from 0 to 100 what is the probability that you will recoup your pawn); pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$); age is age of the borrower in years, +High-school is a dummy that indicates if the client has completed high school. 
}
%\textit{Do file: } \texttt{ss\_balance.do}
\end{table}

@@

\subsection{Analyzing Choice versus Paternalism Using Causal Forests} \label{sec:RF}

>>>>

\title{The forcing-choice design and paternalism in pawnshop borrowing\thanks{We want to thank Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, Anett John, David Laibson, Aprajit Mahajan, Matt Rabin, Mauricio Romero, Charlie Sprenger, Chris Udry, and seminar participants at ITAM, USC, MSU, UC Davis,  UCSD, and USC who provided valuable feedback. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.  Research assistance was financed through faculty grants at ITAM. Our research partner had no say in the design or results of the experiment.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
\date{This draft:  \today \\[2 cm]}

@@

\begin{abstract}
We explore paternalism in the understudied context of high-default pawn lending. We use a novel one-stage, three-armed RCT, including forced and voluntary treatment arms, to point-identify the effects of structured repayment contracts on both the treated and the untreated simultaneously. We find that forcing borrowers into commitment-style contracts decreases the financial cost of pawn loans by 22\% and increases the likelihood of recovering their pawn by 15\%. However, only 11\% of borrowers choose such contracts. We find that borrowers who would not choose regular payments would benefit substantially from getting such contracts, as much as those freely choosing them (no selection on gains).  A paternalistic policy of universal forced commitment archives similar benefits to personalized targeting. 
\end{abstract}

@@

Pawn loans constitute one of the oldest and most common forms of borrowing \citep{carter2012pawnshops}.
Our partner lender, for example, made over 4 million loans to more than a million clients during in the three years adjacent to our experiment.\footnote{For comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.} 
The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{A large literature shows  stress impairs cognitive function, e.g. \cite{StressReview}.}
%\footnote{There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).  \url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.}

@@

Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches. Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing their pawn along with any payments made towards principal.  Indeed, 13\% of those who default first made some payments toward recovery, all of which is lost to them.\footnote{High pawn default rates are common, in the US they oscillate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan. The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent.  In our ``forced commitment'' arm all borrowers are \emph{required} to repay using the same structured monthly contract offered on an opt-in basis in the commitment choice arm. We use the labels commitment and structured payment contract interchangeably.

This design allows us to measure the effects of structured payments, and also the demand for this contractual feature. We demonstrate that it further allows us to estimate the relationship between treatment effects and treatment take-up, a core concern in the econometrics literature. Intuitively, our design can be seen as a two-sided encouragement design, encouraging some borrowers to take and others to not take up structured repayment. In principle, the marginal treatment effect approach allows researchers to use observational data and an excluded instrument to study the relationship between treatment effects and treatment take-up. In practice, unless the instrument has a rich support set, additional modeling assumptions \citep{mogstad2018using} are needed. BDM mechanisms incentivizing choice prior to treatment assignment \citep{becker1964measuring} could be used to tackle this question, with some limitations \citep{bohm1997eliciting,banerji2014detection}. Two-stage Karlan-Zinman designs can be used to study a related question, namely isolating selection and incentive effects in comparing a more and less attractive intervention, such as low- and high-interest credit \citep{KarlanZinman2009} or cash grants versus loans \citep{Beaman2023}. Below we compare our novel one-stage design with these two-stage ones.

@@

On mechanisms, the monthly payment contract seems to achieve these cost savings by speeding up payments and, interestingly, by generating an early \textit{bifurcation} of borrowers into those that will recover the pawn and those that will not. The former are induced to pay faster, saving on interest; the latter pay less towards loans that ultimately default, hence losing less money when they do. One interpretation is that requiring payments earlier accelerates learning about the feasibility of making such payments, thus reducing overconfidence, a mechanism not much discussed in the literature but that appears to be important in our context.

@@

Next, we impose a two-sided exclusion restriction positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it. In other words, we assume that choosing a contract results in the same potential outcome as being assigned that contract. This is a relatively common if often implicit assumption in causal inference.\footnote{Papers that use variation in compulsory schooling laws to identify the returns to schooling, for example, typically interpret their results as the causal effect of additional \emph{education} rather than additional \emph{forced education}. \cite{chamberlain2011bayesian} uses a closely related assumption to develop a theory of optimal treatment choice.} 
It also has testable implications that we fail to reject in our empirical context.\footnote{See \autoref{sec:testing_exclusion} for details.}
Under this restriction, the forcing-choice design point-identifies the TOT, TUT, ASG, ASB, and ASL effects described above.  Our estimated TUT effect on financial cost savings is large: \$192 pesos, equivalent to a 10.6 percentage point savings in APR. On average, the borrowers who would \textit{not} choose commitment, would have faced substantially lower financial costs if they had.

In a one-shot interaction, the game between the borrower and the lender is zero-sum. Decreasing financial costs for the borrower means decreasing the lender's profit. However, we find that experiencing the structured payments contract leads to a 6 percentage point increase in repeat borrowing from the lender. A back-of-the-envelope calculation shows that still, the contract reduces lender's profits by 11\%, implying that lenders would not offer this contract (as was the case in Mexican pawnshops) if not forced in our context.\footnote{Our partner lender contacted us to evaluate structured payments for two reasons. First, they genuinely wanted to know the causal effects of structured payments but did not know how to estimate them rigorously. Second, our lender operates as a non-profit, donating their earnings to philanthropic aims.}

@@

On the question of what explains the persistence of no-commitment contracts so contrary to borrowers’ interests, there are several candidates. From the demand side, while a simple measure of time inconsistency does not explain the large and positive TUT effect, we show substantial levels of over-optimism among borrowers, the average subjective probability of recovering their pawn is 92\%, while the actual average is only 44\%. Among borrowers who do not choose commitment, those with the largest estimated benefits from commitment are the individuals who most systematically over-estimate their own probability of repayment without the need to commit, potentially decreasing their demand from commitment. From the supply side, because loans are over-collateralized, the lender in the contract stands to gain the most when borrowers default.  Our partner's \emph{status quo} pawn contract (standard in the industry) gave 70\% of the value of gold collateral in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract, that could be paid back anytime before the loan comes due at no penalty. The fact that the gold pawn is highly liquid, means that the lender makes more profit over three months from a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid). While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.

@@

Our paper makes a number of contributions to the literature. First, %we propose a way to use three-armed experimental structure to recover treatment effects for choosers and non-choosers under minimal assumptions.\footnote{A companion STATA package provides simple, regression-based estimators for each of these causal parameters, along with appropriate cluster-robust standard errors. See \autoref{sec:estimation_inference} for details.}  
we add to the relatively small literature that sheds light on private paternalism and selection on gains. In the context of food choice,  \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment. In contrast, we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection. In the context of school choice, \cite{Walters} combines a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates. He finds that students who select into more effective schools have smaller treatment effects from attending than those who do not select in. Our approach instead point identifies TUT and TOT and a range of other interesting causal parameters without the need for a structural model, relying instead on relatively weak exclusion restrictions whose testable implications we fail to reject. In the context of agriculture, \cite{Beaman2023} compare the average treatment effect on farm profits from providing \textit{cash grants} to a set of farmers that did not select into getting \textit{loans} to those of average farmers. They do this in a two-stage design, by first offering loans or not to a set of farmers, and then randomizing cash grants among those who would not have received loans. Our paper is complementary in several respects. Because we estimate the average effect of a given treatment for those who did and did not select into that \textit{same} treatment, our design allows us to estimate effects on non-compliers, but on compliers as well, allowing the estimation of selection on gains, selection bias and selection on levels.  \cite{Beaman2023} find that those selecting out of loans have lower average returns to capital, consistent with positive selection. In contrast, we find no evidence of positive selection. Our design can be used in situations where compulsion of the treatment is possible but two-stage randomization is infeasible or too costly.\footnote{\cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they identified \emph{two} TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers. This difference is what allows our design to point identify the ASG and related quantities.}

@@

Our study also speaks to recent research on the effects of payment frequency. While experiments in microfinance markets have \textit{not} not found benefits from providing a more regularized repayment environment as we find here \citep{Pande, barboni2023flexible, Field}, these experiments differ from ours in two important ways: they are performed on top of already highly structured micro-finance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \cite{bauer2012behavioral}. These differences may explain why \citep{Pande} finds almost no default in the control group, in stark contrast to our setting of high default. Second, we study \textit{both} take-up and the efficacy of voluntary commitment mechanisms. A number of papers have found low demand for commitment as we do.\footnote{\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}. Others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).} Unlike all of these papers, however, we separately point-identify and estimate the effects of commitment for borrowers who would and \textit{would not} choose it. Given their enormous prevalence and the vulnerability of their users, pawn loans are severely understudied; we believe the descriptive information and treatment effects estimates for pawn borrowing are an important contribution.

%We also believe that the forcing-choice RCT design provides a useful counterpoint to the widely used \cite{KarlanZinman2009} (KZ) designs. As far as we are aware, ours is the only experimental design in the literature simultaneously estimating both the TOT and TUT effects, along with the average selection on gains, without the need for auxiliary structural assumptions. Note that KZ designs do not estimate the TUT effect, which is crucial for evaluating the case for paternalism.\footnote{The KZ design is useful for separating moral hazard from adverse selection when a two-product comparison is relevant, with one being strictly preferable to consumers.  Our design is useful in mapping marginal treatment effects to compliance with a single treatment, particularly in contexts where a) forcing is possible and b) selection subsequent to forcing is low, or is of direct interest to the principal (in that case, our design would still provide useful information to the principal but would not isolate agent-level heterogeneity in the way it does here).}

The remainder of the paper is structured as follows:  Section \ref{context} provides context and defines our main outcome variables. Section \ref{Design} describes the experiment and data sources, and shows pre-treatment balance across arms. Section \ref{Experiment} provides the standard ITT analysis of the experiment, while Section \ref{Choice} shows how to identify, estimate and carry out inference for the TOT, TUT, ASG, ASB and ASL effects under the forcing-choice design. Section \ref{Paternalism} investigates why paternalism functions so well in this context and whether it can be more finely targeted and Section \ref{conclusion} concludes.

@@

%\hfill \newline
%\noindent \textbf{Borrowers.} 
\paragraph*{Borrowers.} Borrowers are not completely inexperienced: 87\% of clients in our survey report they have pawned before. %These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
However they are economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months. In terms of triggers and uses of the loan, 89\% said they are pawning because of an emergency, and only 12\% stated it was to be used in a ``non-urgent expense''.  When asked why they are pawning this piece, 5\% responded ``lost a family member'', ``a medical emergency'' (11\%), or ``an urgent expense'' (72\%). Only 32\% of borrowers have completed college, 73\% of are women, with an average age of 43 years.

@@

\paragraph*{Gold buying shops.} Gold purchasing shops locate close to our Lender's branches. Branches have an average of \hl{XX} of these shops.  This fact is important given the high default rates which could indicate that borrowers are ex ante intending to `sell' their pawn.  Given that they are receiving 70\% of the value of the pawn next door to shops that would give them 100\% of this value, we think this is prima facie unlikely.

@@

\paragraph*{Overconfidence.} We implemented a baseline survey to more than 6,000 respondents. In it, we asked borrowers for their subjective probability of recovering the pawn. The average recovery probability is 92\%. This contrasts sharply with the actual recovery rate for these same borrowers, 44\%. Overall 72\% of borrowers report a 100\% probability of repaying their loan.    %Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer. 
%Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.

@@

\subsection{No differential selection or imbalance}
\label{sec:integrity}

@@

We were aware that the major threat for this study was selection into borrowing based on contract terms. This did \textit{not} happen. We show this in three different ways. First, out of those coming into the branch and filling out the baseline survey (at which time they did not yet know their treatment status), 97\% end up pawning. This rate is not only high but is virtually identical across treatment arms. Second, the number of loans per day is not different across arms, showing borrowers did not stop pawning when the forcing arm or choice arm was active.  Third, borrower and loan characteristics are the same across arms, showing that there is no selection on observables.\footnote{Note that is borrowers self-selected based on contract terms, the results would still reflect the overall impact of a treatment for the lender's portfolio. In our case, there is no selection, so we can study the causal effects on borrowers.}

@@

Table \ref{attrition_table_final} shows there are no differences in the number of loans, borrowers, or amount borrowed across arms using administrative data. Each row corresponds to a regression of the dependent variable on indicators for treatment assignment (status quo/control, forced commitment, choice). In the first row (``Take-up'') we use the sample of those who answered the baseline survey (6064 subjects) and check which of them pawned based on the administrative data. The dependent variable indicates whether the person pawned. Because this survey was implemented at the entrance of the branch before they knew their treatment assignment, it is a good measure of take-up. The first result is that the overwhelming majority (97\%) take the loan. Second, the same fraction of borrowers take up the loan across treatment arms. This is strong evidence that borrowers did not select deferentially according to the structured payments contractual feature. The remaining rows use only administrative data. For each branch day, we calculate the number of borrowers pawning, the number of pawns used, pawns per borrower, and the total amount borrowed and regress each of those on treatment arms. We again cannot reject that any of those measures of demand are the same across arms.  We also report medians to reduce the influence of outliers.

\begin{table}[H]
\caption{No selection across arms}
\label{attrition_table_final}
\begin{center}
\footnotesize{\input{./Tables/Attrition.tex}}
\end{center}
\scriptsize{Each row in this table 
 corresponds to a regression at the branch-day level of each dependent variable against the experimental arms indicators (control, forced commitment, choice). The table reports the coefficients on each of these indicators, as well as the p-value of an F-test of the null hypothesis of equality of the three coefficients. We also report a median regression for each arm. %Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.
 }
%\textit{Do file: } \texttt{ss\_att.do}
\end{table}

@@

\begin{table}[H]
\caption{Borrower's characteristics are balanced}
\label{SS_final}
\begin{center}
\resizebox{0.65\textwidth}{!}{
\footnotesize{\input{./Tables/SS.tex}}
}
\end{center}
\scriptsize {Each row in this table corresponds to a regression, where the level of observation is a borrower that pawned which was surveyed.  \hl{Surveys were not conducted at the beginning of the experiment}. The dependent variables are displayed in the first column. Each dependent variable is regressed against the experimental arms indicators (control, forced commitment, choice). The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients. ``Subjective value'' of the pawn refers to how much would the client be willing to sell the pawn for in pesos, ``Trouble paying bills'' is an indicator for the borrower reporting having problems paying electricity, water and services in the last 6-months, present bias is constructed as in \cite{Ashraf}; ``Makes buget'' os an indicator for whether the household make expenses budget for the month ahead of time. The subjective probability of recovery was elicited a la Manski (from 0 to 100 what is the probability that you will recoup your pawn); pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$); age is age of the borrower in years, +High-school is a dummy that indicates if the client has completed high school. 
}
%\textit{Do file: } \texttt{ss\_balance.do}
\end{table}

@@

\subsection{Targeting Paternalism using Causal Forests} \label{sec:RF}
